Manuscript

### 2018-10-24 manuscript.Rmd
new fxn for all CRISPR genes in drug screens

```{r}
library(bsselectR)
library(data.table)
library(ggpubr)
library(ggsignif)
library(kableExtra)
library(tidyverse)
```

@@

```{r}
WilcoxonByDrug <- function(drug, dataset, data_name) {
  use_data <- filter(dataset, Drug == drug)
  sig <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Hugo_Symbol", data = use_data, method = "wilcox.test", p.adjust.method = "BH")
  sig <- adj_signif(sig)
  sig <- sig[order(sig$p),]
  sig$Drug <- drug
  sig$Dataset <- data_name
  return(sig)
}
```

@@

g2p_genes
g2p_drugs
# Order and genes taken from pink heatmapo from Daniel's analyses
g2p_genes <- c("KRAS", "EGFR", "MET", "ALK", "BRAF", "ERBB2", "ABL1", "ROS1", "KIT", "DPYD", "PDGFRA", "RET", "BRCA1", "UGT1A1", "IDH2", "ESR1", "TPMT", "BRCA2", "PDGFRB", "G6PD", "PML", "TSC1", "FLT3", "ERBB3", "CYP19A1", "AKT1", "PTCH1", "MGMT", "DNMT3A", "MYD88", "PDGFB", "TSC2", "NPM1", "JAK2")
```

@@

# CCLE
ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
ccle <- merge(drug_meta, ccle, by = "CID")
ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "AUC")
ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = g2p_genes)
ccle_data <- merge(ccle_grid, ccle_melt, by = "accession_id", all.x = TRUE)
ccle_data <- merge(ccle_data, ccl_converter, by = "accession_id", all.x = TRUE)
ccle_data <- merge(ccle_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
ccle_data$Mutation_Status_Nonsilent <- ifelse(is.na(ccle_data$Mutation_Status_Nonsilent), "Other", ccle_data$Mutation_Status_Nonsilent)
ccle_data$Hugo_Symbol <- factor(ccle_data$Hugo_Symbol)
ccle_data$AUC <- as.numeric(ccle_data$AUC)
ccle_data$Color_Nonsilent <- ifelse(ccle_data$Mutation_Status_Nonsilent == "Other", "palegreen3", "springgreen4")
ccle_data$Color_Nonsilent <- factor(ccle_data$Color_Nonsilent)
ccle_data <- filter(ccle_data, !is.na(ccle_data$AUC))
ccle_data$Drug_Gene <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol)
saveRDS(ccle_data, "./data_munging/rds/ccle_data_18Q3.rds", compress = "xz")

# CTRP
ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
ctrp <- merge(drug_meta, ctrp, by = "CID")
ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = g2p_genes)
ctrp_data <- merge(ctrp_grid, ctrp_melt, by = "accession_id", all.x = TRUE)
ctrp_data <- merge(ctrp_data, ccl_converter, by = "accession_id", all.x = TRUE)
ctrp_data <- merge(ctrp_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
ctrp_data$Mutation_Status_Nonsilent <- ifelse(is.na(ctrp_data$Mutation_Status_Nonsilent), "Other", ctrp_data$Mutation_Status_Nonsilent)
ctrp_data$Hugo_Symbol <- factor(ctrp_data$Hugo_Symbol)
ctrp_data$AUC <- as.numeric(ctrp_data$AUC)
ctrp_data$Color_Nonsilent <- ifelse(ctrp_data$Mutation_Status_Nonsilent == "Other", "slategray3", "steelblue4")
ctrp_data$Color_Nonsilent <- factor(ctrp_data$Color_Nonsilent)
ctrp_data <- filter(ctrp_data, !is.na(ctrp_data$AUC))
ctrp_data$Drug_Gene <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol)
saveRDS(ctrp_data, "./data_munging/rds/ctrp_data_18Q3.rds", compress = "xz")

# GDSC
gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
gdsc <- merge(drug_meta, gdsc, by = "CID")
gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = g2p_genes)
gdsc_data <- merge(gdsc_grid, gdsc_melt, by = "accession_id", all.x = TRUE)
gdsc_data <- merge(gdsc_data, ccl_converter, by = "accession_id", all.x = TRUE)
gdsc_data <- merge(gdsc_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
gdsc_data$Mutation_Status_Nonsilent <- ifelse(is.na(gdsc_data$Mutation_Status_Nonsilent), "Other", gdsc_data$Mutation_Status_Nonsilent)
gdsc_data$Hugo_Symbol <- factor(gdsc_data$Hugo_Symbol)
gdsc_data$AUC <- as.numeric(gdsc_data$AUC)
gdsc_data$Color_Nonsilent <- ifelse(gdsc_data$Mutation_Status_Nonsilent == "Other", "paleturquoise3", "turquoise4")
gdsc_data$Color_Nonsilent <- factor(gdsc_data$Color_Nonsilent)
gdsc_data <- filter(gdsc_data, !is.na(gdsc_data$AUC))
gdsc_data$Drug_Gene <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol)
saveRDS(gdsc_data, "./data_munging/rds/gdsc_data_18Q3.rds", compress = "xz")
```

```{r}
ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q3.rds")
ccle_data_ptmuts <- filter(ccle_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele_Length == 1 | is.na(ccle_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)

ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q3.rds")
ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele_Length == 1 | is.na(ctrp_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)

gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q3.rds")
gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele_Length == 1 | is.na(gdsc_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)

@@

# Gene mutation frequency

```{r}
crispr_data_g2p_summ <- unique(crispr_data_g2p[, c("Hugo_Symbol", "N_Nonsilent_Mutant", "N_Nonsilent_Other")])
crispr_data_g2p_summ$Fraction_Mutant <- crispr_data_g2p_summ$N_Nonsilent_Mutant / (crispr_data_g2p_summ$N_Nonsilent_Mutant + crispr_data_g2p_summ$N_Nonsilent_Other)
crispr_data_g2p_summ$Percent_Mutant <- crispr_data_g2p_summ$Fraction_Mutant * 100
# write.table(crispr_data_g2p_summ, file = "~/Desktop/crispr_data_g2p_summ_20181003.tsv", quote = FALSE, sep = "\t")
```

@@

## CRISPR: Gene

@@

crispr_data_signif_g2p_gene_plot <- ggplot(data = crispr_data_signif_g2p_gene, aes(x = Mutation_Status_Nonsilent, y = Score)) +
  facet_wrap(~ Hugo_Symbol, nrow = 2, scales = "free_y") +
  geom_jitter(aes(color = Mutation_Status_Nonsilent), alpha = 0.5, width = 0.3) +
  geom_boxplot(color = "black", fill = NA, outlier.shape = NA) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  scale_color_manual(values = crispr_data_signif_g2p_gene_color) + 
  geom_text(data = crispr_data_signif_g2p_gene_text, mapping = aes(x = 1.5, y = Text_y, label = p.signif), nudge_y = 0.2) +
  theme(legend.position = "top") +
  labs(y = "CERES Score",
       x = "Lineage",
       color = "Mutation Status",
       title = "CERES scores for select Level A G2P genes",
       subtitle = "Genes are sorted by increasing p-value.")
crispr_data_signif_g2p_gene_plot
# Genes with adjusted p-values < 0.3 are shown.\nBH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\n
# ggsave("./plots_18Q3/manuscript/crispr_data_signif_g2p_gene_plot.png", crispr_data_signif_g2p_gene_plot, width = 12, height = 7, units = "in")
```

## CRISPR: Gene and lineage

@@

>>>>

```{r}
library(bsselectR)
library(data.table)
library(ggpubr)
library(ggsignif)
library(kableExtra)
library(reshape2)
library(tidyverse)
```

@@

```{r}
WilcoxonByDrug <- function(drug, dataset, data_name) {
  use_data <- filter(dataset, Drug == drug)
  sig <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Hugo_Symbol", data = use_data, method = "wilcox.test", p.adjust.method = "BH")
  sig <- adj_signif(sig)
  sig <- sig[order(sig$p),]
  sig$Drug <- drug
  sig$Dataset <- toupper(data_name)
  return(sig)
}

WilcoxonByDrugAllGenes <- function(melt_file, grid_file, data_name) {
  druglist <- as.character(unique(melt_file$Drug))
  sig_df <- NULL
  for(i in 1:length(druglist)) {
    print(paste0("Current drug in process: ", druglist[i], " (drug ", i, " of ", length(druglist), ")."))
    flush.console()
    melted <- filter(melt_file, Drug == druglist[i])
    use_data <- merge(grid_file, melted, by = "accession_id", all.x = TRUE)
    use_data <- merge(use_data, ccl_converter, by = "accession_id", all.x = TRUE)
    use_data <- merge(use_data, maf_df, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
    use_data$Mutation_Status_Nonsilent <- ifelse(is.na(use_data$Mutation_Status_Nonsilent), "Other", use_data$Mutation_Status_Nonsilent)
    use_data$Hugo_Symbol <- factor(use_data$Hugo_Symbol)
    use_data$AUC <- as.numeric(use_data$AUC)
    use_data <- filter(use_data, !is.na(use_data$AUC))
    use_data$Drug_Gene <- paste0(use_data$Drug, "_", use_data$Hugo_Symbol)
    use_data_ptmuts <- filter(use_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
    use_data_ptmuts$Keep_PtMut_Tests <- ifelse(use_data_ptmuts$Reference_Allele_Length == 1 | is.na(use_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(use_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
    use_data_ptmuts <- filter(use_data_ptmuts, Keep_PtMut_Tests == TRUE)

    sig <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Hugo_Symbol", data = use_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
    sig <- adj_signif(sig)
    sig <- sig[order(sig$p),]
    sig <- filter(sig, p <= 0.05)
    sig$Drug <- druglist[i]
    sig$Dataset <- toupper(data_name)
    sig_df <- rbind(sig_df, sig)
  }
  return(sig_df)
}
```

@@

g2p_genes
g2p_drugs
# Order and genes taken from pink heatmapo from Daniel's analyses
g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
```

@@

# CCLE
ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
ccle <- merge(drug_meta, ccle, by = "CID")
ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "AUC")
ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = g2p_genes)
ccle_data <- merge(ccle_grid, ccle_melt, by = "accession_id", all.x = TRUE)
ccle_data <- merge(ccle_data, ccl_converter, by = "accession_id", all.x = TRUE)
ccle_data <- merge(ccle_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
ccle_data$Mutation_Status_Nonsilent <- ifelse(is.na(ccle_data$Mutation_Status_Nonsilent), "Other", ccle_data$Mutation_Status_Nonsilent)
ccle_data$Hugo_Symbol <- factor(ccle_data$Hugo_Symbol)
ccle_data$AUC <- as.numeric(ccle_data$AUC)
ccle_data$Color_Nonsilent <- ifelse(ccle_data$Mutation_Status_Nonsilent == "Other", "palegreen3", "springgreen4")
ccle_data$Color_Nonsilent <- factor(ccle_data$Color_Nonsilent)
ccle_data <- filter(ccle_data, !is.na(ccle_data$AUC))
ccle_data$Drug_Gene <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol)
saveRDS(ccle_data, "./data_munging/rds/ccle_data_18Q3_g2pgenes.rds", compress = "xz")

# CTRP
ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
ctrp <- merge(drug_meta, ctrp, by = "CID")
ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = g2p_genes)
ctrp_data <- merge(ctrp_grid, ctrp_melt, by = "accession_id", all.x = TRUE)
ctrp_data <- merge(ctrp_data, ccl_converter, by = "accession_id", all.x = TRUE)
ctrp_data <- merge(ctrp_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
ctrp_data$Mutation_Status_Nonsilent <- ifelse(is.na(ctrp_data$Mutation_Status_Nonsilent), "Other", ctrp_data$Mutation_Status_Nonsilent)
ctrp_data$Hugo_Symbol <- factor(ctrp_data$Hugo_Symbol)
ctrp_data$AUC <- as.numeric(ctrp_data$AUC)
ctrp_data$Color_Nonsilent <- ifelse(ctrp_data$Mutation_Status_Nonsilent == "Other", "slategray3", "steelblue4")
ctrp_data$Color_Nonsilent <- factor(ctrp_data$Color_Nonsilent)
ctrp_data <- filter(ctrp_data, !is.na(ctrp_data$AUC))
ctrp_data$Drug_Gene <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol)
saveRDS(ctrp_data, "./data_munging/rds/ctrp_data_18Q3_g2pgenes.rds", compress = "xz")

# GDSC
gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
gdsc <- merge(drug_meta, gdsc, by = "CID")
gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = g2p_genes)
gdsc_data <- merge(gdsc_grid, gdsc_melt, by = "accession_id", all.x = TRUE)
gdsc_data <- merge(gdsc_data, ccl_converter, by = "accession_id", all.x = TRUE)
gdsc_data <- merge(gdsc_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
gdsc_data$Mutation_Status_Nonsilent <- ifelse(is.na(gdsc_data$Mutation_Status_Nonsilent), "Other", gdsc_data$Mutation_Status_Nonsilent)
gdsc_data$Hugo_Symbol <- factor(gdsc_data$Hugo_Symbol)
gdsc_data$AUC <- as.numeric(gdsc_data$AUC)
gdsc_data$Color_Nonsilent <- ifelse(gdsc_data$Mutation_Status_Nonsilent == "Other", "paleturquoise3", "turquoise4")
gdsc_data$Color_Nonsilent <- factor(gdsc_data$Color_Nonsilent)
gdsc_data <- filter(gdsc_data, !is.na(gdsc_data$AUC))
gdsc_data$Drug_Gene <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol)
saveRDS(gdsc_data, "./data_munging/rds/gdsc_data_18Q3_g2pgenes.rds", compress = "xz")
```

```{r}
ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q3_g2pgenes.rds")
ccle_data_ptmuts <- filter(ccle_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele_Length == 1 | is.na(ccle_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)

ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q3_g2pgenes.rds")
ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele_Length == 1 | is.na(ctrp_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)

gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q3_g2pgenes.rds")
gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele_Length == 1 | is.na(gdsc_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)

@@

@@

## CRISPR: G2P genes

@@

crispr_data_signif_g2p_gene_plot <- ggplot(data = crispr_data_signif_g2p_gene, aes(x = Mutation_Status_Nonsilent, y = Score)) +
  facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 2, scales = "free_y") +
  geom_jitter(aes(color = Mutation_Status_Nonsilent), alpha = 0.5, width = 0.3) +
  geom_boxplot(color = "black", fill = NA, outlier.shape = NA) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  scale_color_manual(values = crispr_data_signif_g2p_gene_color) + 
  geom_text(data = crispr_data_signif_g2p_gene_text, mapping = aes(x = 1.5, y = Text_y, label = p.signif), nudge_y = 0.2) +
  theme(legend.position = "top") +
  labs(y = "CERES Score",
       x = "Lineage",
       color = "Mutation Status",
       title = "CERES scores for select Level A G2P genes",
       subtitle = "Genes are sorted by increasing p-value.")
crispr_data_signif_g2p_gene_plot
# Genes with adjusted p-values < 0.3 are shown.\nBH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\n
# ggsave("./plots_18Q3/manuscript/crispr_data_signif_g2p_gene_plot.png", crispr_data_signif_g2p_gene_plot, width = 12, height = 7, units = "in")
```

## CRISPR: G2P genes and lineage

@@

## Drug screens: All CRISPR genes

Drug metadata:
```{r}
drug_meta <- read.delim("./data_munging/drug_id_drug_name_table_10_12_2018.tsv", sep = "\t", header = FALSE)
colnames(drug_meta) <- c("CID", "Drug")
drug_meta$Drug <- tolower(drug_meta$Drug)
```

CCLE:
```{r, eval=FALSE}
ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
ccle <- merge(drug_meta, ccle, by = "CID")
ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "AUC")
ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
ccle_data_allgenes <- WilcoxonByDrugAllGenes(ccle_melt, ccle_grid, "CCLE")
saveRDS(ccle_data_allgenes, "./data_munging/rds/ccle_data_18Q3_allgenes.rds", compress = "xz")
```

CTRP:
```{r, eval=FALSE}
ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
ctrp <- merge(drug_meta, ctrp, by = "CID")
ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
ctrp_data_allgenes <- WilcoxonByDrugAllGenes(ctrp_melt, ctrp_grid, "CTRP")
saveRDS(ctrp_data_allgenes, "./data_munging/rds/ctrp_data_18Q3_allgenes.rds", compress = "xz")
```

GDSC:
```{r, eal=FALSE}
gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
gdsc <- merge(drug_meta, gdsc, by = "CID")
gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
gdsc_data_allgenes <- WilcoxonByDrugAllGenes(gdsc_melt, gdsc_grid, "GDSC")
saveRDS(gdsc_data_allgenes, "./data_munging/rds/gdsc_data_18Q3_allgenes.rds", compress = "xz")
```

# Dataset summaries

```{r}
crispr_data_g2p_summ <- unique(crispr_data_g2p[, c("Hugo_Symbol", "N_Nonsilent_Mutant", "N_Nonsilent_Other")])
crispr_data_g2p_summ$Percent_Mutant <- crispr_data_g2p_summ$N_Nonsilent_Mutant / (crispr_data_g2p_summ$N_Nonsilent_Mutant + crispr_data_g2p_summ$N_Nonsilent_Other) * 100
rownames(crispr_data_g2p_summ) <- NULL
# write.table(crispr_data_g2p_summ, file = "~/Desktop/crispr_data_g2p_summ_20181003.tsv", quote = FALSE, sep = "\t")

knitr::kable(crispr_data_g2p_summ, caption = "CRISPR: Level A G2P genes mutation status summary") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

```{r fig.height=4, fig.width=8}
g2p_druggene_p_summ <- g2p %>% group_by(Drug_Gene) %>% tally()
g2p_druggene_p_summ <- merge(g2p_druggene_p_summ, ccle_signif_g2p[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
g2p_druggene_p_summ <- merge(g2p_druggene_p_summ, ctrp_signif_g2p[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE, suffixes = c("_CCLE", "_CTRP"))
g2p_druggene_p_summ <- merge(g2p_druggene_p_summ, gdsc_signif_g2p[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
colnames(g2p_druggene_p_summ)[colnames(g2p_druggene_p_summ) == "p_CCLE"] <- "CCLE"
colnames(g2p_druggene_p_summ)[colnames(g2p_druggene_p_summ) == "p_CTRP"] <- "CTRP"
colnames(g2p_druggene_p_summ)[colnames(g2p_druggene_p_summ) == "p"] <- "GDSC"
g2p_druggene_p_summ_melt <- melt(g2p_druggene_p_summ, id.vars = c("Drug_Gene", "n"), measure.vars = c("CCLE", "CTRP", "GDSC"), variable.name = "Dataset", value.name = "p")

g2p_druggene_p_summ_plot <- ggplot(data = g2p_druggene_p_summ_melt, aes(x = p, y = n, shape = Dataset, color = Dataset)) +
  geom_point(size = 2) +
  geom_smooth(method = "lm", se = FALSE, lwd = 0.5) +
  scale_color_manual(values = c("green3", "darkslategray4", "darkturquoise")) +
  labs(x = "Gene-drug association p-value by mutation status", y = "Number of level A G2P associations")
g2p_druggene_p_summ_plot
# ggsave("./plots_18Q3/manuscript/g2p_druggene_p_summ_plot", g2p_druggene_p_summ_plot.png, device = "png", dpi = 450, width = 8, height = 4, units = "in")
```
